\chapter{About the author}
Marian Schneider was born on October 10\textsuperscript{th} 1988 in Oldenburg, Germany. He graduated from high school at Gymnasium Eversten Oldenburg in 2008. He subsequently was admitted to the Bachelor program of Maastricht University College, the Netherlands, where he completed courses in psychology, economics, philosophy and neuroscience. In 2011, he spent an Erasmus semester at the Institut d'\'Etudes Politiques in Toulouse, France. He received a Bachelor of Arts (summa cum laude) in 2012. Next, he enrolled in the Research Master program in Cognitive Neuroscience at Maastricht University. In 2013, he was awarded a scholarship by the German Academic Scholarshipip Foundation ('Studienstiftung des deutschen Volkes'). For his Master thesis, he investigated layer-specific attention effects in human primary visual cortex using 7 Tesla magnetic resonance imaging. This research was conducted from 2013 to 2014 under the supervision of Prof. Dr. Nikolaus Weiskopf at the Wellcome Trust Centre for Neuroimaging, University College London, United Kingdom. He obtained a Master of Science (cum laude) and his master thesis won the prize for the best thesis of the Faculty of Psychology and Neuroscience in 2014. Funded by an NWO TopTalent grant, he conducted his doctoral research from 2014 to 2019 under supervision of Dr. Federico De Martino, Prof. Dr. Nikolaus Weiskopf, and Prof. Dr. Rainer Goebel at the Department of Cognitive Neuroscience, Faculty of Psychology and Neuroscience, Maastricht University. Marian currently lives in Tallinn, Estonia, where he founded a one-man business and does freelance work for BrainInnovation to develop deep neural net architectures for tissue class segmentation of the human brain.