\chapter{Acknowledgments}
This thesis would not have been possible without the help and continuous support of many people, who I hold very dear.

I would like to thank my supervisory team. \textbf{Federico}, I know you always read this section of the thesis with great attention. So be assured that these lines have been chosen carefully for you. I am grateful for many things that you have done for me but two of them in particular. First, that you did not run away when I asked you to join my supervisory team. You are the best academic closer in town: I don't think there is a single piece of research that goes unpublished in your hands and it was this push towards completing work that enormously benefited this PhD project and, I know, many PhD projects before that. Second, I am grateful that no matter what happened, no matter how desperate the situation appeared (\textit{to me}), you kept on reminding me that the most important thing in science (and life) is to be a good fellow human. This mindset came in many different guises and it meant that I did not just feel like another student of yours but like a family friend, always welcome in your home. May the cores of your computer always be busy.

\textbf{Rainer}, I am extremely grateful that, almost from the first time we met (I was giving a presentation on 3D GRASE in your Advanced fMRI course), you placed your trust in my abilities. I am not sure what it was that you saw in me but I am glad that it kicked off a successful cooperation over many years. No matter how high the target, you always seemed to think that I was up to the job. I am also very thankful that  this trust, together with your tireless efforts to remove every formal obstacle in my way, provided for an environment where I had the luxury to dedicate almost all my time and mental resources to research. Finally, I would like to thank you for informal discussions and ideas that turned out to be very influential for my thinking on the future of (artificial) consciousness. May your optimism prevail in times of light and in times of darkness.

\textbf{Nikolaus}, thank you for welcoming me to your lab, for introducing me to basic (down to the tone!) and more advanced topics of MRI, for supervising my first steps in academia, for being such a patient and encouraging teacher, and for inspiring professionalism wherever you go. May your kindness and professionalism define the future of academic research. 

I would like to thank my brothers in arms, \textbf{Ingo} and \textbf{Faruk}. When I was deciding where to do the PhD, there were many aspects that weighed into my decision. One thing that I totally underestimated was the influence of peers. As the ancient German proverb has it "even a blind chicken sometimes finds a grain to pick" - indicating that even undeserving people sometimes get lucky. I guess, in this case, the chicken (me) was not only blind but also headless and got more than lucky. I am tremendously indebted to our (meta) journeys to foreign lands, during which we saw blunt swords and shiny armor, profound abysses and mountains of hope, monkey parades and acts of great human humbleness (or did we?), exotic acronym animals, mind palaces and gipsy houses. May your thirst for exploration never die and your fountains of knowledge never run dry.

\textbf{Yawen}, *in general*, you are a good person. In particular, I am thankful that life gave me a new friend (and such a loyal one, at that!) in the very last moments of my Maastricht life. Thank you for introducing me to the sinosphere (especially the mooncakes) and for tirelessly tearing down the cultural barriers between us. May your cosmopolitan spirit take over the world.

\textbf{Mario}, dr. dr. amigo, my most competent friend and breaker of the chain of causation that keeps your free will unfree. I am not being ironic here - or am I? I guess it doesn't matter as long as it is "just" in my mind. Thank you for all the exciting discussions about our bionic future, extraordinary life advice and the many private GP sessions. May your spirit remain unconditionally free.

My PhD sisters, \textbf{Geraldine} and \textbf{Linda}, thank you for all the dinners, cocktails and a few memorable nights of dancing in the Sway. \textbf{Geraldine}, amiga, may your lust for life brighten a many peoples' mood. \textbf{Linda}, may your pointed remarks make many more people smile and may the dancing continue.

My PhD brothers, \textbf{Franc} and \textbf{Sri}, thank you for keeping me company. \textbf{Franc}, may your moustache make a reappearance. \textbf{Sri}, may you never run out of "chill pill" catchphrases.

Thank you to the senior generation of PhD students - \textbf{Valentin}, \textbf{Thomas}, \textbf{Mario} and \textbf{Arko} - all of them honorable gentlemen for being living and breathing examples of the future. May your good manners inspire generations to follow.

\textbf{Jessica}, I am grateful for all the time spent together and the discussions we had - in university buildings and on pique-nique blankets in the park. May your critical mind inconvenience the establishment.

\textbf{Tyler}, the friendly visitor from Glasgow. Thank you for all the balanced discussions. May your voice of reason be heard.

\textbf{Dimo}, thank you for all the help and support at the scanner. May your sequences continue to run flawlessly. 

\textbf{Joel} - even though our paths only crossed shortly, I am thankful for the things that you taught me. May your example lead the way.

Thank you to \textbf{the Dutch people and state}, for providing near-Utopian conditions for living and doing research. May your model of the welfare state and open exchange of goods and ideas outlast right-wing populism.

Thanks to the \textbf{European Union} for giving me the freedom of movement. May you be populated with citizens that appreciate you.

Danke an meine Familie, \textbf{Claudia}, \textbf{Norbert} und \textbf{Sarah}, für Eure bedingungslose Unterstützung und unermüdliche Fürsorge. Wenn man in einer bildungsnahen Umgebung wie der Euren aufwächst, könnte man all die erfolgreichen Schul- und Uniabschlüsse fast als Selbstverständlichkeit erachten. Das sind sie natürlich nicht und ich bin für den Rückhalt, den Ihr mir über all die Jahre gegeben habt, ausgesprochen dankbar. Möge die Selbstverständlichkeit, mit der Ihr Bildung unterstützt und ermöglicht habt, die normalste Sache der Welt werden.

\textbf{Undine}, thank you for all your love and sparkles. It has been a tremendous pleasure to evolve together with you over all those years, from the kids we were at UCM to what almost feels like proper adults. I am thankful to have in you an honest friend, a supportive partner and a mobile family. May you always be my home in the world, no matter where we are.

{\flushright \thesisauthor \\ Maastricht \\ \thesisdate \\ }